---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(readr)
library(tidyverse)
library(googlesheets4)

#read in proportion data
np_url <- "https://docs.google.com/spreadsheets/d/1hfK3ptAkMU4AiM5PknHe4IebFl29wEWNdMKpc5nEC4M/edit#gid=0"
np_data <-
  read_sheet(np_url) %>% 
  left_join(read_sheet(np_url, sheet = 2)) %>% 
  print()

houston_url <- "https://docs.google.com/spreadsheets/d/1-VpDe1FBQKK1nWYI_HOV8qVGD1fSHKUoe65E11iqOEU/edit#gid=1776011343"

houston_data <-
  read_sheet(houston_url) %>% 
  left_join(read_sheet(houston_url, sheet = 2)) %>% 
  print()

#year 2020 data
NP_Species_20 <- read_sheet("https://docs.google.com/spreadsheets/d/1rVNHuyM9z6qAGKWknkn8j7zuJhFyHJeZnLgxxVdpM-4/edit#gid=0")
NP_Species_20


Houston_Species_20 <- read_sheet("https://docs.google.com/spreadsheets/d/1E4_RjXlmtJN9BJ0-z-cDE3Mzdpym_Bl0bLrklUKAsu8/edit#gid=0")

#year 2018 data
NP_Species_18 <- read_sheet("https://docs.google.com/spreadsheets/d/1bBaDxI7PnZIbDDT4N_kmLap8wHPJO6cyj4Qaxv3xwvI/edit#gid=0")
NP_Species_18

houston_url <-"https://docs.google.com/spreadsheets/d/1dE-9shHj4D0H8DHCF25JeJpycBEBOA5x38j4uQILnJs/edit#gid=0"

Houston_Species_18 <- 
read_sheet(houston_url, sheet = "data")

#2021 data
NP_Species <- read_sheet("https://docs.google.com/spreadsheets/d/1hfK3ptAkMU4AiM5PknHe4IebFl29wEWNdMKpc5nEC4M/edit#gid=0")
NP_Species

Houston_Species <- read_sheet("1-VpDe1FBQKK1nWYI_HOV8qVGD1fSHKUoe65E11iqOEU")

```

#Title

Author

Affiliations

Abstract

The Minnesota State University of Moorhead Regional Science Center has two established restored prairie sites: North Pond and Houston. Students at MSUM have collected 5 years of percent cover data from North Pond and 3 years from Houston. We will be using these data sets to ask "How does species richness vary in native restored prairies when NPK fertilizer treatments are applied?" We will be using exploratory data analysis to pursue this question by comparing percent cover and taxa data from both sites to look at the variation of species richness. Previous studies on native and restored prairies have shown that anthropogenic influences on the environment fuel the growth of invasive species (MacDougall et al. 2014). We expect to find that plots with applied NPK fertilizer will have a lower overall species richness than plots with no nutrients applied. A greater understanding of these processes and consequent environmental impacts may provide a useful background of knowledge for land management, restoration, and conservational efforts.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}

#manipulate rows
data <-
  bind_rows(
    np_data, 
    houston_data
  ) %>% 
  mutate(
    plot = factor(plot)
  )


data_presence_site <- 
  data %>% 
  distinct(site, status) %>% 
  mutate(present = TRUE) %>% 
  pivot_wider(
    names_from = "site", 
    values_from = "present", 
    values_fill = FALSE
  ) 

data %>% 
  count(site, plot, status, name = "n_spp") %>% 
  group_by(site) %>% 
  mutate(n_site = sum(n_spp), p = n_spp/n_site) %>% 
  group_by(status, site) %>% 
  summarise(sum_p = sum(p)) %>% 
  ggplot() +
  geom_col(mapping = aes(x = site, y = sum_p, fill = status),
           position = "stack")

```

```{r}

data <-
  bind_rows(
    NP_Species, 
    Houston_Species
  ) %>% 
  mutate(
    plot = factor(plot)
  )

data_presence_site <- 
  data %>% 
  distinct(site, taxa) %>% 
  mutate(present = TRUE) %>% 
  pivot_wider(
    names_from = "site", 
    values_from = "present", 
    values_fill = FALSE
  )

data %>% 
  count(site, plot, treatment, name = "n_spp") %>% 
  ggplot() +
  geom_col(mapping = aes(x = plot, y = n_spp, fill = treatment)) +
  facet_wrap(~ site)
```

```{r}

data <-
  bind_rows(
    NP_Species_20, 
    Houston_Species_20
  ) %>% 
  mutate(
    plot = factor(plot)
  )

data_presence_site <- 
  data %>% 
  distinct(site, taxa) %>% 
  mutate(present = TRUE) %>% 
  pivot_wider(
    names_from = "site", 
    values_from = "present", 
    values_fill = FALSE
  ) 

#FOR POSTER
data %>% 
  count(site, plot, treatment, name = "n_spp") %>% 
  ggplot() +
  geom_col (size = 3) + (mapping = aes(x = plot, y = n_spp, fill = treatment)) +
  facet_wrap(~ site)
```

```{r}

data <-
  bind_rows(
    NP_Species_18, 
    Houston_Species_18
  ) %>% 
  mutate(
    plot = factor(plot)
  )

data_presence_site <- 
  data %>% 
  distinct(site, taxa) %>% 
  mutate(present = TRUE) %>% 
  pivot_wider(
    names_from = "site", 
    values_from = "present", 
    values_fill = FALSE
  )  

#FOR POSTER
data %>% 
  count(site, plot, treatment, name = "n_spp") %>% 
  ggplot() +
  geom_col (size = 3) + (mapping = aes(x = plot, y = n_spp, fill = treatment)) +
  facet_wrap(~ site)
```
